\documentclass[11pt, oneside]{article}

\usepackage{geometry}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{color}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{hyperref,cleveref}

\newcommand{\templatedoc}[1]{{\color{gray}:#1}}

% add other people here 

\newcommand{\harsha}[1]{{\color{green!40!blue}[\textbf{Harsha}:#1]}}
\newcommand{\martin}[1]{{\color{blue!20!red}[\textbf{Martin}:#1]}}
\newcommand{\matthijs}[1]{{\color{blue}[\textbf{Matthijs}:#1]}}
\newcommand{\georgew}[1]{{\color{orange}[\textbf{GeorgeW}:#1]}}
\newcommand{\dmitry}[1]{{\color{blue!50!purple}[\textbf{Dmitry}:#1]}}

\iffalse 

\newcommand{\harsha}[1]{}
\newcommand{\martin}[1]{}
\newcommand{\matthijs}[1]{}

\fi

\newtheorem{definition}{Definition}
\newcommand{\recall}[2]{${#1}$-recall$@{#2}$} 


\title{
\vspace{-40pt}
  Billion-Scale Approximate Nearest Neighbor Search Challenge}
\author{
\hspace{-20pt}  \footnotesize{Harsha Vardhan Simhadri}  \thanks{Lead organizers. Harsha will coordinate standard hardware tracks T1, T2. George will coordinate specialized hardware track T3.} \\ \hspace{-20pt} \scriptsize{Microsoft Research India} \\ \hspace{-20pt} \scriptsize{\tt harshasi@microsoft.com} \and
\hspace{-25pt}  \footnotesize{George Williams}\footnotemark[1] \\ \hspace{-25pt} \scriptsize{GSI Technology} \\ \hspace{-25pt} \scriptsize{\tt gwilliams@gsitechnology.com} \and
\hspace{-25pt}  \footnotesize{Martin Aum\"uller}\thanks{Organizer names listed alphabetically by surname.} \\\hspace{-30pt} \scriptsize{IT University of Copenhagen} \\ \hspace{-25pt} \scriptsize{\tt maau@itu.dk}  \and
\hspace{-25pt}  \footnotesize{Artem Babenko}\footnotemark[2] \\ \hspace{-40pt} \scriptsize{Yandex} \\ \hspace{-40pt} \scriptsize{\tt artem.babenko@phystech.edu} \and
\hspace{-20pt}  \footnotesize{Dmitry Baranchuk}\footnotemark[2] \\ \hspace{-20pt} \scriptsize{Yandex} \\ \hspace{-20pt} \scriptsize{\tt dbaranchuk@yandex-team.ru} \and
\hspace{-20pt}  \footnotesize{Qi Chen}\footnotemark[2] \\ \hspace{-20pt} \scriptsize{Microsoft Research Asia}\\ \hspace{-20pt} \scriptsize{\tt cheqi@microsoft.com} \and
\hspace{-20pt}  \footnotesize{Matthijs Douze}\footnotemark[2] \\ \hspace{-15pt} \scriptsize{Facebook AI Research} \\ \hspace{-20pt} \scriptsize{\tt matthijs@fb.com} \and
\hspace{-20pt}  \footnotesize{Ravishankar Krishnaswamy}\footnotemark[2] \\ \hspace{-20pt} \scriptsize{MSR India, IIT Madras} \\ \hspace{-20pt} \scriptsize{\tt rakri@microsoft.com} \and
  \footnotesize{Gopal Srinivasa}\footnotemark[2] \\\scriptsize{Microsoft Research India} \\ \scriptsize{\tt gopalsr@microsoft.com} \and
  \footnotesize{Suhas Jayaram Subramanya}\footnotemark[2] \\\scriptsize{Carnegie Mellon University}\\ \scriptsize{\tt suhasj@cs.cmu.edu} \and
  \footnotesize{Jingdong Wang}\footnotemark[2] \\\scriptsize{Microsoft Research Asia}\\ \scriptsize{\tt jingdw@microsoft.com} 
}
%% \date{\today}

\begin{document}
\maketitle
\vspace{-20pt}
\begin{abstract}
  Despite the broad range of algorithms for Approximate Nearest
  Neighbor Search, most empirical evaluations of algorithms have
  focused on smaller datasets (1 million points). However, deploying
  recent advances in embedding based techniques for search,
  recommendation and ranking at scale require ANNS indices at billion,
  trillion or larger scale. Barring a few recent papers, there is
  limited consensus on which algorithms are effective at this scale
  vis-\`a-vis their hardware cost.  We propose to set up a leaderboard
  of ANNS algorithms on representative billion scale datasets and
  compare algorithms by hardware cost, accuracy and performance. We
  will use two recent indexing algorithms DiskANN~\cite{DiskANN19} and
  FAISS~\cite{Faiss17} as baselines.  We will solicit entries from
  theorists and practitioners from across communities who have worked
  on ANNS, encourage new approaches that minimize hardware costs, and
  compare the relative merits of the algorithms objectively and
  subjectively.  We will provide Azure cloud compute credit to make
  the competition inclusive for participants without necessary
  infrastructure. The anticipated impact is an understanding of the
  ideas that apply at billion+ scale, bridging communities that work
  on ANNS problems, and a platform for newer researchers to contribute
  and develop this relatively new research area.
\end{abstract}

\subsection*{Keywords}
Embeddings, Retrieval, Search, Approximate Nearest Neighbor Search, Billion scale.
\subsection*{Competition type} Regular.

\input{competition}
\input{organization}
\input{resources}



\bibliographystyle{plain}
\bibliography{ref}


\end{document}
